\plaintitle

### 2016-04-22 paper/paper.tex
Small changes to paper, compiled

\section{Visualization}\label{sec:visualization}
The visualization consists of three parts:
\paragraph{The bubble view} a compact view on the play-offs per season
\paragraph{The statistics (zoom) view} a more detailed view on a statistic of a selected 
team
\paragraph{The team view} a detailed view on how good or bad a team scores on a specific 
field position
All three are discussed in more detail below. The three views are available to
the user on a single webpage. The user start on the bubble view and is able to
navigate to the statistics and team views by scrolling down or clicking on
teams.
%The webpage is built in such a way that it gives a hint to the user at the bottom
%or the top of a page when another view is available. By showing a different 
%background color and an arrow, we invite the visitor to explore other views. The 
%user is also at liberty to scroll through these views. However, a fixed scroll is
%implemeted so users will only end in complete views when moving around. Note that 
%the user also will be guided through all 3 views when performing actions described 
%in the section below.

@@

\subsection{The statistics view}
The statistics view gives a user a clear overview of how a statistic has been 
influenced compared to the year before. The view consists of 3 parts:
\paragraph{Context section} the top part should inform the user of his/her context.
\paragraph{Arrow section} This section illustrates why a statistic changed
\paragraph{Small multiples section} Small multiples of team statistics and how they evolve over time
\subsubsection{Context section}
The context section should inform the user at all times of the current selections 
that have been made. The statistics view will always be based on a specific team
and season that have been selected or that are initated. This should be clear based
on the textual information in the top left. Next to that, in the top right a small 
bubble view is shown. It indicates the team selected and how well it performed in 
the play-offs during that season. When changing teams and/or season, this view gets 
updated as well as the textual information.

@@

\section{Lessons learned}\label{sec:discussion}
We've learned a couple of lessons during the creation of this visualization:
- Find a use case as soon as possible to built your visualization around
- Each separate component should be a sufficient informative visualization on itself
- Creating a custom visualization costs time and opportunities
In what follows we will discuss our experience in more detail.

@@

\begin{appendices}

    \section{Terminology}\label{sec:terminology}

    \paragraph{PER} Player Efficiency Rating - An all-in-one basketball rating,
    boiling down all of a player's contributions into one number\cite{per}.
\end{appendices}

>>>>

\section{Visualization}\label{sec:visualization}
The visualization consists of three parts:
\begin{itemize}
    \item The bubble view: a compact view on the play-offs per season
    \item The statistics (zoom) view: a more detailed view on a statistic of a
        selected team
    \item The team view: a detailed view on how good or bad a team scores on a
        specific field position
\end{itemize}
All three are discussed in more detail below. The three views are available to
the user on a single webpage. The user start on the bubble view and is able to
navigate to the statistics and team views by scrolling down or clicking on
teams.
%The webpage is built in such a way that it gives a hint to the user at the bottom
%or the top of a page when another view is available. By showing a different 
%background color and an arrow, we invite the visitor to explore other views. The 
%user is also at liberty to scroll through these views. However, a fixed scroll is
%implemeted so users will only end in complete views when moving around. Note that 
%the user also will be guided through all 3 views when performing actions described 
%in the section below.

@@

\subsection{The statistics view}
The statistics view gives a user a clear overview of how a statistic has been 
influenced compared to the year before. The view consists of 3 parts:
\begin{itemize}
    \item Context section: the top part should inform the user of his/her
        context.
    \item Arrow section: This section illustrates why a statistic changed
    \item Small multiples section: Small multiples of team statistics and how
        they evolve over time
\end{itemize}
\subsubsection{Context section}
The context section should inform the user at all times of the current selections 
that have been made. The statistics view will always be based on a specific team
and season that have been selected or that are initated. This should be clear based
on the textual information in the top left. Next to that, in the top right a small 
bubble view is shown. It indicates the team selected and how well it performed in 
the play-offs during that season. When changing teams and/or season, this view gets 
updated as well as the textual information.

@@

\section{Lessons learned}\label{sec:discussion}
We've learned a couple of lessons during the creation of this visualization:
\begin{itemize}
    \item Find a use case as soon as possible to build your visualization around
    \item Each separate component should be a sufficient informative visualization on itself
    \item Creating a custom visualization costs time and opportunities
\end{itemize}
In what follows we will discuss our experience in more detail.

@@

\appendix
\section{Terminology}\label{sec:terminology}

\paragraph{PER} Player Efficiency Rating - An all-in-one basketball rating,
boiling down all of a player's contributions into one number\cite{per}.
